Combinatorial interpretations of~holonomic recurrences

### 2021-09-13 article/main.tex
Remove done todo
Spellcheck

\begin{definition}
    Let \(n\) be the length of the sequence \(\enc{T}\). Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as a~suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\). Note that the suffix may be an ordered forest.\todo{add to the example}
\end{definition}

@@

\begin{itemize}
    \item node is a~virtual leaf (each tree with \(n\) actual nodes has exactly \((n + 1)\) places where such contex apply):\\
        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_001}%
    \item node is an~actual node (tree with \(n\) actual nodes has excatly \(n\) places where such context apply):\\
        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_002}%
    \item node is a~root (each tree has exactly \(1\) place where such context apply):\\
        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_003}%
    \item node has its parent on the left, i.e.~is right child of its parent (the node can be specified to be actual or virtual):\\
        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004}%
        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004b}%
    \item node has its parent on the right, i.e.~is the left child of its parent (the node can be specified to be actual or virtual):\\
        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_005}%
        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_005b}%
\end{itemize}

@@

We will be operating on transformation classes, sections. They will start being empty and we will be adding tranformations to them.

>>>>

\begin{definition}
    Let \(n\) be the length of the sequence \(\enc{T}\). Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as a~suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\). Note that the suffix may be an ordered forest.
\end{definition}

@@

\begin{itemize}
    \item node is a~virtual leaf (each tree with \(n\) actual nodes has exactly \((n + 1)\) places where such context apply):\\
        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_001}%
    \item node is an~actual node (tree with \(n\) actual nodes has exactly \(n\) places where such context apply):\\
        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_002}%
    \item node is a~root (each tree has exactly \(1\) place where such context apply):\\
        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_003}%
    \item node has its parent on the left, i.e.~is right child of its parent (the node can be specified to be actual or virtual):\\
        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004}%
        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004b}%
    \item node has its parent on the right, i.e.~is the left child of its parent (the node can be specified to be actual or virtual):\\
        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_005}%
        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_005b}%
\end{itemize}

@@

We will be operating on transformation classes, sections. They will start being empty and we will be adding transformations to them.
